---
title: "How Does Algeria compare to other Arab Countries in doing business?  "
author: "Bekioua Fateh"
date: "October 15, 2016"
output: html_document
---



###Getting Doing Business Data from Worrld Bank Website  

```{r, message = FALSE, warning=FALSE}
library(dplyr)
library(googleVis)
op <- options(gvis.plot.tag='chart')
library(tidyr)
library(DT)
link <- "http://databank.worldbank.org/data/download/DB_CSV_en.zip"
download.file(link, destfile = "db.zip")
```
Unzipping and reading the Data
```{r,message = FALSE, warning=FALSE}
db <-read.csv(unz("db.zip",filename = "DB_Data.csv"),stringsAsFactors = TRUE)
```
Show the data structure and the top 100 row

```{r, message = FALSE, warning=FALSE}
str(db)
datatable(db[1:100,])
```



###Preparing the Data  
Changing the name of the first variable  
Creating a vector to store Arab Countries names  

```{r, message = FALSE, warning=FALSE}

names(db)[1]<- "Country.Name"
arabs<- c("Algeria", "Tunisia", "Egypt, Arab Rep.", "Jordan", "Kuwait",
         "Lebanon", "Middle East & North Africa","Morocco","Oman","Qatar",
         "Saudi Arabia","Sudan","United Arab Emirates","Yemen, Rep.",
         "Bahrain")
         
```

Selecting only the needed variables for our analysis  
Filtring to get only the Arab Countries and  
Removing records with missing data  

```{r, message = FALSE, warning=FALSE}
db_arab<- db %>%
        select(1,3,10:15) %>%
        filter(Country.Name %in% arabs) %>%
        na.omit()
```

Showing the data structure and the top 100 row after the data filtration  

```{r, message = FALSE, warning=FALSE}
str(db_arab)
datatable(db_arab[1:100,])
```

Gathering the years variables into one column in order to have one line per country and year  
```{r, message = FALSE, warning=FALSE}
db_arab <- gather(db_arab, year, value , 3:8)
datatable(db_arab[1:100,])
```

Spreading the indicator column into multiple columns in order to have one indicator per column  
```{r, message = FALSE, warning=FALSE}
db_arab <- spread(db_arab, Indicator.Name, value)
datatable(db_arab[1:100,])
```

Removing all the indicators with missing values in order to compare countries by commun indicator  


```{r, message = FALSE, warning=FALSE}
present<-(sapply(db_arab, function(x)!any(is.na(x))))
db_arab<-db_arab[, present]
db_arab$year<- as.numeric(substr(db_arab$year, 2,6))
datatable(db_arab)
```

### Ploting the motion chart
```{r, results='asis',message = FALSE, warning=FALSE}
chart<- gvisMotionChart(db_arab, idvar="Country.Name", 
                        timevar= "year", yvar = "Time required to connect to electricity (days)",
                        xvar = "Procedures required to start a business (number)",
                        colorvar = "Time required to start a business (days)",
                        sizevar = "Tax payments (number)",
                        options=list(width=1024, height=600))
plot(chart)
options(op)
```

Please note that the Motion Chart is only displayed when hosted on a web server, or if placed in a directory which has been added to the trusted sources in the security settings of Macromedia. See the googleVis package vignette for more details